---
title: "ag_data"
output: html_document
date: "2022-11-07"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(readxl)
```

## Start by reading the data

```{r}
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx", col_names = TRUE)
```

## Get the column names and index them

```{r}
cnames <- colnames(strawb) 
x <- 1:dim(strawb)[2]
```

## drop the columns with only one unique value

```{r}
## Set T as an indicator
T <- NULL

## Collect number of unique rows in each column
for(i in x){T <- c(T, dim(unique(strawb[i]))[1])}

## Use T to select columns to drop --
drop_cols <- cnames[which(T == 1)]

## Now, drop the columns with only one unique value.
strawb %<>% select(!all_of(drop_cols))
```


## Let's arrange the data frame and separate data item.

```{r}
strawb %<>% arrange(Year, State)

## now look at the `Data Item` column
temp1 <- strawb %>% select(`Data Item`) %>% distinct()

## separate by dash at first and then separate by comma
strawb2 <- strawb %>% separate(col=`Data Item`, 
                               into = c("temp1","temp2"), 
                               sep = "-", fill = "right") %>% 
  separate(col=`temp2`, 
           into = c("sales", "units", "avg"), 
           sep = ",", 
           fill = "right")

## create column for organic strawberry
strawb2 %<>% mutate(organic=ifelse(str_detect(strawb2$temp1,"ORGANIC"),1,0),
                    .after=temp1)
```

## clean column for strawb2

```{r}
strawb2 %<>% mutate(avg = ifelse(is.na(avg),0,1))
strawb2$temp1 <- gsub("STRAWBERRIES, ORGANIC","", as.character(strawb2$temp1))
strawb2$temp1 <- gsub("STRAWBERRIES","", as.character(strawb2$temp1))
strawb2$temp1 <- gsub(",","", as.character(strawb2$temp1))
colnames(strawb2)[6] <- "condition"

strawb_raw <- strawb 
strawb <- strawb2
```


## clean env

```{r}
rm(strawb2, temp1)
```

## get organic and non organic strawberries

```{r}
org_row <- which(strawb$organic==1) 
strawb_organic <- strawb %>%
  slice(org_row, preserve = FALSE) 
strawb_non_organic <- strawb %>%
  filter(!row_number() %in% org_row)
```

## grep chemical rows

```{r}
chem_rows <- grep("APPLICATIONS", strawb_non_organic$sales, ignore.case = T)

chem_rows_1 <- grep("chemical", strawb_non_organic$Domain, ignore.case = T)

ins <- intersect(chem_rows, chem_rows_1)

chem_rows_2 <- grep("chemical", strawb_non_organic$`Domain Category`, ignore.case = T)

ins_2 <- intersect(chem_rows, chem_rows_2)
```

## make strawberries applied with chemicals

```{r}
strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
```

## first drop the "no-info" columns Since we will need to do this
## for all three tibbles, write a functin

```{r}
before_cols = colnames(strawb_chem) 
T = NULL 
x = length(before_cols)

for(i in 1:x){ 
  b <- length(unlist(strawb_chem[,i] %>% unique()) ) 
  T <- c(T,b) }

drop_cols <- before_cols[which(T == 1)] 
strawb_chem %<>%
  select(!all_of(drop_cols)) 

after_cols = colnames(strawb_chem)
```

## separate Domain Category at :

```{r}
strawb_chem %<>% separate(col=`Domain Category`, 
                          into = c("dc1", "chem_name"), 
                          sep = ":", fill = "right")

temp1 <- strawb_chem %>% select(chem_name) %>% unique()
length(unlist(temp1))

sum(strawb_chem$Domain == strawb_chem$dc1) == dim(strawb_chem)[1]
```

## clean up columns

```{r}
strawb_chem %<>% select(Year, State, units, avg, dc1, chem_name, Value)
```

## remove "MEASURED IN"

```{r}
strawb_chem$units <- str_remove_all(strawb_chem$units, "MEASURED IN ")
```

## Separate fertilizers from strawb_chem table

```{r}
bb <- grep("CHEMICAL,", strawb_chem$dc1, ignore.case = T) 
length(bb)
chem <- 1:2112 
non_chem_rows <- setdiff(chem, bb)
length(non_chem_rows)

temp1 <- strawb_chem %>% slice(non_chem_rows) 
fertilizers <- temp1

rm(temp1, bb)
```

## now remove "CHEMICAL," from the entries in the dc1
## and rename the column chem_types

```{r}
strawb_chem$dc1 <- str_remove_all(strawb_chem$dc1, "CHEMICAL,")

strawb_chem$dc1 %>% unique()

strawb_chem %<>% rename(chem_types = dc1)
```



## remove the parens

```{r}
strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\(")

strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\)")
```

## separate chem_name and chem_code

```{r}
strawb_chem %<>% separate(col = chem_name, 
                          into = c("chem_name","chem_code"), 
                          sep = "=", fill = "right" )
```

## check for NAs and there is only missing chemical code

```{r}
unique(is.na(strawb_chem))
```

## get specific chemical tables
## BIFENTHRIN table

```{r}
bb <- grep("BIFENTHRIN", strawb_chem$chem_name, ignore.case = T)

bifen <- strawb_chem %>% slice(bb)
```

## methyl bromide table

```{r}
cc <- grep("methyl bromide", strawb_chem$chem_name, ignore.case = T)

methyl <- strawb_chem %>% slice(cc)
```

## chloropicrin table

```{r}
ch <- grep("chloropicrin", strawb_chem$chem_name, ignore.case = T)

chloropicrin <- strawb_chem %>% slice(ch)

rm(bb,cc,ch)
```

## filter the chloropicrin level in CA through years

```{r}
ca_chlor <- chloropicrin %>% filter(State=="CALIFORNIA", units==" LB")
ca_chlor$Value <- as.integer(ca_chlor$Value)
ca_chlor$Year <- as.integer(ca_chlor$Year) 
ca_chlor %<>% select(Year, Value) 
ca_chlor %>% ggplot(aes(Year, Value)) + 
  geom_bar(stat="identity")
```



## Gradescope problem
## 1 {#section}
## get rows that cwt==285

```{r}
ans_1 <- which(strawb$Value==285) 
cat("By examining around 615 rows, we found $87015 for the corresponding value.")
```

## 2 {#section-1}
## examine target rows

```{r}
strawb %>% filter(State=="CALIFORNIA" & Year==2016 & Domain=="ORGANIC STATUS") 
range <- 231304956*1.96*0.137 
lower <- 231304956-62110007
upper <- 231304956+62110007 
cat("The CI is (169194949, 293414963)")
```

## 3

```{r}
cat("The CI is (111691147, 192065033)")

```

## 4

```{r}
strawb_chem %>% group_by(State) %>% summarize(count_distinct = n_distinct(chem_name)) 
ans_4 <- length(unique(strawb_chem$chem_name))
cat("172 for total, 139 for California, 116 for Florida")
```

## 5
## find chem count by states

```{r}
strawb_chem %>% group_by(State) %>% summarize(count_distinct = n_distinct(chem_name))
ans_5 <- 139-116 
cat("CA has chemical number of", ans_5)
```


